
\begin{document}

\chapter{Context Survey}

\label{chapter:contextsurvey}

For years the planning community has been developing algorithms that allow
robots to navigate through environments to reach a goal. As research
progressed, so did the complexity of the environments that the robots needed to
move through. It started with static obstacles which remain stationary for the
entirety of the execution, then on to dynamic obstacles with stochastic motion,
to dynamic obstacles that have predictable paths that planners can exploit. For
the last situation, a number of planners implementing different techniques have
been created. Techniques include evolutionary computation on geometric
structures in space-time to generate paths, safe interval path planning,
sampling based space-time search using collision prediction, and probabilistic
methods. Note that this context survey only covers approaches that make use of
models of obstacle behaviour and discards approaches that purely react to
obstacle motion.

\section{Evolutionary Algorithms}

Wang et al.\ used a genetic algorithm~\cite{galletly1992overview} that would
generate a path around the static and dynamic obstacles~\cite{wang2007mobile}.
The obstacles were encoded by a set of vertices in a polygon. The chromosomes
used in the genetic algorithms represented the paths that the robot can take to
move to the goal where the path is comprised of the initial and goal points
along with obstacle vertices.  The path generated for the robot would cling to
the perimeters of obstacles, until the robot could move towards the goal
similar to the bug algorithm~\cite{weir}. The time at which the robot would
reach each node was also encoded into the path. Moving obstacles were
represented as static obstacles for a given time. Upon a sensed change in the
environment such as a dynamic obstacle veering off its prescribed trajectory,
the genetic algorithm was used to regenerate a collision free path.

Smierzchalski and Michalewicz have also used an evolutionary
approach~\cite{evosurvey} where the chromosome represents the spatio temporal
path in order to plan the movements of a ship in a harbour where the obstacles
are other ships in shipping lanes~\cite{smierzchalski2005path}. The higher the
evaluation for the chromosome (i.e.\ the path) the safer and shorter the path
is. Unlike the work done by Wang et al.\ the path can be comprised of any point
in the search space.  The obstacles were represented geometrically and the
dynamic obstacles were represented by their initial configuration and velocity.
Since the path represented in a spatio-temporal fashion, the genetic algorithm
is able to determine if a path will collide with a dynamic obstacle by deducing
where the dynamic obstacle will be at each time step along the path and
checking for a collision.  Replanning using the evolutionary algorithm was
implemented to account for obstacles deviating from their prescribed
trajectories.

Dunwei and Na used particle swarm optimization (PSO)~\cite{kennedy2010particle}
to generate local paths around dynamic obstacles that are represented by
trajectory bands~\cite{dunwei2011local}.  In order to account for the
stochasticity in the obstacle trajectories, a distance around each obstacle's
trajectory was used to describe how much the obstacle can deviate from it.
Using these bands, an objective function was created that represents the safety
of a generated path and PSO was used to generate a path that could minimize the
objective function.

\section{Safe Interval Path Planning}

Narayanan et al.\ and Phillips et al.\ have developed algorithms for generating
safe paths to guide a robot to a goal configuration by determining time
intervals for which it would be safe to travel through certain areas in the
search space and using a graph search algorithm to find a path to the goal that
only intersects safe time intervals~\cite{asipp, sipp}.  Safe time intervals
are determined by iterating through the trajectory of each obstacle and
updating a query structure that can be used to check whether a certain space
will be free for a given period of time. A lattice structure is used to
discretize the search space and an A* variant, Anytime Reparing A*
(ARA*)~\cite{likhachev2003ara} is used to search this lattice. This algorithm
relies on the robot waiting at certain locations for areas to become free of
obstacles before it is able move towards the goal.

\section{Sampling in Space-time}

Berg et al.\ have developed a sampling based approach that generates a
probabilistic roadmap of the same dimension as the configuration space of the
robot with time that takes into account static and dynamic obstacles.
\cite{van2006anytime}. A novel graph search technique similar to D*
Lite~\cite{koenig2002d} was implemented that can automatically repair the path
when new information about obstacle motion is available such that the robot
will not be led into a collision with an obstacle. Obstacles are represented by
elongated objects in space-time and their stochasticity is represented by their
size as the time away from the current time increases.

Hsu et al.\ have also created an algorithm that generates a probabilistic
roadmap in space-time where each node represents the configuration of the robot
and a time at which the robot would be at the
configuration~\cite{hsu2002randomized}. Using the probabilistic roadmap, a
shortest path algorithm is used to find the fastest route from the initial
configuration of the robot to the goal configuration. Obstacles are represented
in a similar fashion as the work done by Berg et al.~\cite{van2006anytime}
except there is no representation of stochasticity. The planner handles updated
information about the dynamic obstacles by updating the probabilistic roadmap
and researching the graph for a path to the goal.

\section{Probabilistic Methods}

Jensen et al.\ developed an algorithm that uses a probabilistic obstacle model
to represent and employs a gradient decent method to find a path to the
goal~\cite{jensen2003motion}. A gradient decent approach tries to minimize the
probability of the robot coming into collision with an obstacle along the path.
This method is general but assumes that the robot has a sensing radius and is
able to move in the direction that has the lowest probability of collision.
Likewise, the paper shows that the combined probability model for the obstacles
in the scene only has one global minima. The algorithm can also be adapted so
that there is a trade off between the probability of collision and the length
of the path.

Rodriguez et al.\ uses a dynamic probabilistic roadmap to find a global path to
the goal and local kinodynamic motion planning to evade dynamic
obstacles~\cite{rodriguez2007framework}. A self-repairing probabilistic roadmap
is generated that takes into account the location of static obstacles. Using
this roadmap, a global path to the goal is found using a graph search
technique. The global path represents a sequence of sub-goal regions and a
kinodynamic local planner using an approach similar to RRT~\cite{rrt}
determines the local path that moves the robot to each sub-goal region in
sequence. This approach allows obstacles which have been assumed to be
stationary to move or have uncertainty in their positions. The probabilistic
roadmap will automatically repair itself upon obtaining updated information
about the static obstacles such that no edge is in collision with an obstacle.

\section{Limitations of Related Work}

The main limitation of the developments described is that there is no solution
that uses the obstacles' known stochastic trajectories to build probabilistic
representations and use these representations to build complete low cost paths.
Some of the algorithms currently either assume that the planner only knows that
the obstacles will move randomly around a point~\cite{rodriguez2007framework}
or that the obstacles will move along a fixed
trajectory~\cite{hsu2002randomized}, and if they deviate, a new plan is
developed. Hsu et al.\ assumed perfect information about the obstacle
trajectories to build an initial path through the environment, and if the
information was incorrect or the obstacles deviate from their prescribed
trajectories, the planner develops a new route to the goal. Berg et al.\
increased the size of the dynamic obstacles in space time to account for random
motion, but to plan around them, represented the obstacles as static objects in
space-time thus not devising a cost metric for their motion. Likewise, the
approaches that used safe interval path planning~\cite{asipp, sipp}, did not
build probabilistic models of the obstacles, but instead determined intervals
at which it would be safe to travel through certain areas and is thus heavily
reliant on the robot waiting at certain locations. The evolutionary approaches
described were geometric and also did account for the stochasticity in the
known trajectories of the dynamic obstacles. The one approach that did create
probabilistic models of the dynamic obstacles~\cite{jensen2003motion} employed
a gradient decent method similar to that of potential fields that is described
in Sec.~\ref{sec:costpf} to be ineffective in certain situations and that a
sampling based approach is more complete. All of these approaches lack an
elegant, sampling based algorithm that can take into account the stochastic
trajectories of dynamic obstacles in order to rely less heavily on replanning,
and to make use of the available information from the environment. The approach
described in this work develops a formal representation dynamic obstacles that
is able to take into account their stochasticity and presents a novel sampling
based approach that is able to generate low cost paths that can lead a robot to
its goal.

\end{document}
